Peer influences in air travel behavior: A social autoregressive analysis

### 2015-05-23 article/article.Rmd
Added code to calculate friends within an arbitrary radius.

```{r distance_from_atlanta, eval=FALSE}
cities <- read.csv("data/PRIVATEDATA/geocode/geocoded_datatables/allcities.csv")%>%
  tbl_df()

>>>>

```{r distance_from_atlanta, eval=FALSE}
# how many friends are within different distances?
friends_distance <- friends %>%
  group_by(id) %>%
  summarise(
    friends_win_10 = sum(miles_from_atl < 10, na.rm = TRUE),
    friends_win_25 = sum(miles_from_atl < 25, na.rm = TRUE),
    friends_win_50 = sum(miles_from_atl < 50, na.rm = TRUE),
    friends_win_100 = sum(miles_from_atl < 100, na.rm = TRUE)
    )

user <- user %>%
  left_join(friends_distance)
```

A descriptive summary of the data is given in Table .
